% !TEX program = xelatex

\documentclass{resume}

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Jacob Hell}

\basicInfo{
  \email{jakehell95@gmail.com} \textperiodcentered\ 
  \phone{256-417-3608} \textperiodcentered\ 
  \linkedin[jacob-hell]{https://www.linkedin.com/in/jacob-hell}}

\section{\faUsers\ Experience}
\datedsubsection{\textbf{Dynetics} Huntsville, Alabama}{Sep 2019 -- Present}
\role{Computer Analyst 3}

Brief introduction: Wrote software supporting UA (Unmanned Aircraft) testing.
\begin{itemize}
  \item Created desktop applications using Java with JavaFX and Swing.
  \item Developed tools to graphically display UA data, such as location.
  \item Wrote software to listen to UA protocol traffic and convert and send to new locations.
  \item Established requirements with customers.
  \item Gave technical demonstrations to customers.
  \item Resolved bugs filed by customers and developers.
\end{itemize}

\datedsubsection{\textbf{Hexagon Geospatial} Huntsville, Alabama}{Jun 2017 -- Sep 2019}
\role{Software Analyst}

Brief introduction: Served as a key developer for the Oversize/Overweight (OSOW) permitting solution for Hexagon's transportation group.
\begin{itemize}
  \item Worked with hybrid .NET and Java based applications that use C\# and Java on the server-side, Oracle as the back-end database and ExtJS for the front-end UI.
  \item Designed and implemented processes to migrate customer data from existing permitting systems.
  \item Supported customers through the software release cycle, including pre go live and go live activites.
  \item Wrote scripts to assist in the CI/CD pipeline.
  \item Resolved bugs filed by customers and QA team.
  \item Implemented new features for existing code bases.
\end{itemize}

\datedsubsection{\textbf{Stetson University} DeLand, Florida}{May 2016 -- May 2017}
\role{Web Application Developer}

Brief introduction: Member of the Enterprise Information Systems team, helped develop and maintain web applications that are widely used by students and faculty.
\begin{itemize}
  \item Functioned as a full stack developer, working with Java, Spring MVC, PL/SQL, and JQuery.
  \item Converted existing PHP applications to Java.
  \item Developed internal tools for use by other developers.
  \item Fixed application bugs reported by end users.
  \item Implmeneted new software requested by administration.
\end{itemize}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: Java, C\#, SQL, Javascript, Python
  \item Platform: Windows, Linux
  \item Editors: Eclipse, Visual Studio, vim
\end{itemize}

%tried using bibtex but couldn't get it so it would look good enough. Might look into later
\section{\faFlask\ Research}
\begin{itemize}[parsep=0.5ex]
\item Hell, Jacob, Michael Clay, and Hala ELAarag. "Hierarchical dungeon procedural generation and optimal path finding based on user input." Journal of Computing Sciences in Colleges 33.1 (2017): 175-183.
\end{itemize}
\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Stetson University}, DeLand, FL}{2013 -- 2017}
\textit{Bachelors of Science} in Computer Science (B.S.)
\end{document}
