% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Jacob Hell}

\basicInfo{
  \email{jakehell95@gmail.com} \textperiodcentered\ 
  \phone{256-417-3608} \textperiodcentered\ 
  \linkedin[jacob-hell]{https://www.linkedin.com/in/jacob-hell}}

\section{\faUsers\ Experience}
\datedsubsection{\textbf{Hexagon Geospatial} Huntsville, Alabama}{Jun 2017 -- Present}
\role{Software Analyst}
Brief introduction: Serve as a key developer for the Oversize/Overweight (OSOW) permitting solution for Hexagon's transportation group.
\begin{itemize}
  %\item Worked with hybrid .NET and Java based applications that use C\# and Java on the server-side, Oracle as the back-end database and ExtJS for the front-end UI.
  \item Designed and implemented processes to migrate customer data from existing permitting systems.
  \item Supported customers through the software release cycle, including pre go live and go live activites.
  \item Wrote scripts to assist in the CI/CD pipeline.
  \item Resolved bugs filed by customers and QA team.
  \item Implemented new features for existing code bases.
\end{itemize}

\datedsubsection{\textbf{Stetson University}}{May 2016 -- May 2017}
\role{Web Application Developer}
Brief introduction: Member of the Enterprise Information Systems team, helped develop and maintain web applications that are widely used by students and faculty.
\begin{itemize}
  \item Functioned as a full stack developer, working with Java, Spring MVC, PL/SQL, and JQuery.
  \item Converted existing PHP applications to Java.
  \item Developed internal tools for use by other developers.
  \item Fixed application bugs reported by end users.
  \item Implmeneted new software requested by administration.
\end{itemize}

\datedsubsection{\textbf{Stetson University}}{Aug 2015 -- May 2016}
\role{Computer Science Tutor}
Brief introduction: Computer science tutor for the math and computer science department.
\begin{itemize}
  \item Worked one on one with other students taking introductory level computer science classes.
  \item Examined and recommended solutions for student assignments and projects.
  \item Explained the facets of Java and basic computer science principles.
\end{itemize}

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
%  \item Programming Languages: Java, C\#, SQL, Javascript, Python
  \item Platform: Windows, Linux
  \item Editors: Eclipse, Visual Studio, vim
\end{itemize}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Stetson University}, Deland, FL}{2013 -- 2017}
\textit{Bachelors of Science} in Computer Science (B.S.)

\section{\faVial\ Research}
\bibliographystyle{IEEETran}
\bibliography{mycite}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
